Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2023-07-30 ba_resubmit_template_files/kundinger_resubmit3.tex
update brian's file.

We estimate the posterior distribution of the parameters in (\ref{eqn:likelihood} - \ref{eqn:pi}) using a Gibbs sampler. Appendix \ref{app:derivations} presents derivations for the full conditional distributions. We initialize $\bm{m}$, $\bm{u}$ and $\pi$ from random draws from their prior distributions, and initialize $\bm{Z}$ to reflect no matches across data files; that is, $\bm{Z} = (n_A + 1, \ldots, n_A + n_B)$. Denote the current draw of the sampler by $(s)$ and the updated draw by $(s+1)$. To update $\bm{m}_f$ and $\bm{u}_f$ for all $f = 1, \ldots, F$, we sample
\begin{subequations}
\begin{align}
	\bm{m}_f^{(s+1)}|\gamma, \bm{Z}^{(s)}, \bm{u}^{(s)}, \pi^{(s)} &\sim \text{Dirichlet}(\alpha_{f1}(\bm{Z}^{(s)}), \ldots, \alpha_{fL_f}(\bm{Z}^{(s)})), \label{eqn:m_update} \\
	\bm{u}_f^{(s+1)}|\gamma, \bm{Z}^{(s)}, \bm{m}^{(s)}, \pi^{(s)} &\sim \text{Dirichlet}(\beta_{f1}(\bm{Z}^{(s)}), \ldots, \beta_{fL_f}(\bm{Z}^{(s)})), \label{eqn:u_update} \\
	\text{where }\alpha_{fl}(\bm{Z}^{(s)})&= \alpha_{fl} + \sum_{i=1}^{n_A}\sum_{j=1}^{n_B} I_{obs}(\gamma_{ij}^f) I(\gamma_{ij}^f = l) I(Z_j^{(s)} = i), \label{eqn:alpha_update} \\
	\text{and } \beta_{fl}(\bm{Z}^{(s)})&=  \beta_{fl} + \sum_{i=1}^{n_A}\sum_{j=1}^{n_B}  I_{obs}(\gamma_{ij}^f) I(\gamma_{ij}^f = l) I(Z_j^{(s)} \neq i) \label{eqn:beta_update}.
	%where $\alpha_{fl}(\bm{Z}^{(s)})= \alpha_{fl} + \sum_{i,j} I_{obs}(\gamma_{ij}^f) I(\gamma_{ij}^f = l) I(Z_j^{(s)} = i)$, and $\beta_{fl}(\bm{Z}^{(s)})= \\ \beta_{fl} + \sum_{i,j} I_{obs}(\gamma_{ij}^f) I(\gamma_{ij}^f = l) I(Z_j^{(s)} \neq i)$.
\end{align}
\end{subequations}
Next, we sample $\pi$ from its full conditional, given by
\begin{align}
	\pi^{(s+1)}|\gamma, \bm{Z}^{(s)}, \bm{m}^{(s+1)}, \bm{u}^{(s+1)} \sim  \text{Beta}(n_{AB}(\bm{Z}^{(s)}) + \alpha_{\pi}, n_B - n_{AB}(\bm{Z}^{(s)}) + \beta_{\pi}).
\end{align}
where $n_{AB}(\bm{Z}^{(s)}) = \sum_{j=1}^{n_B} I(Z_j^{(s)} \leq n_A)$.

@@

Finally, to obtain an estimate $\hat{\bm{Z}}$ of the linkage structure, we use the loss functions and Bayes estimate from \cite{sadinle_bayesian_2017}. Since (\ref{eqn:fast_beta_prior}) does not strictly enforce one-to-one matching, it is possible for this Bayes estimate to link multiple records in $B$ to one record in $A$. To obtain a Bayes estimate that fulfills the bipartite requirement, we minimize the expected loss subject to the constraint that $\hat{Z}_j \neq \hat{Z}_{j'}$ for all $j \neq j'$. See Appendix \ref{bayes-estimate} for details redarding the initial Bayes estimate and this post-processing procedure.

@@

We then map the integers in \eqref{eqn:hashing} to sequential integers $\{1, \ldots, P\}$. Denote each unique agreement pattern as $h_p = (h_p^1, \ldots, h_p^F)$, and the set of unique agreement patterns as $\mathcal{P} = \{h_1, \ldots, h_P\}$. When the $(i,j)$ record pair exhibits agreement pattern $p$, we say $\gamma_{ij} = h_p$. In calculations, we will at times use the one-hot encoding of agreement pattern $h_p$, denoted $e(h_p)$. This is a vector of length $\sum_{f=1}^F L_f$ in which the $l + \sum_{k=1}^{f-1} L_k$ component is 1 when $\gamma_{ij}^f = l$, and 0 otherwise. 
%A more complete example of the one-hot encoding is provided in Appendix \ref{app:ohe}.

@@

	In Figure \ref{fig:speed2}, where we fix $n_B = 500$, we see near linear growth for the run-time under \texttt{BRL} as $n_A$ increases, and much more static run-time under \texttt{fabl}. The slight increases in run-time for \texttt{fabl} are due primarily to the hashing step, which again can be run in parallel for large data. To illustrate that these trends are generalizeable to other specifications of the comparison vectors, we have included the run-time results for an additional simulation study, under different comparison vector settings, in Appendix \ref{app:appendix-speed}.

@@

	We create comparison vectors according to the default settings of the \texttt{compareRecords} function from the \texttt{BRL} package, shown in Table \ref{Tab:sadinle_simulation_cutoffs}. Each simulation identifies matched individuals between two data files, each with 500 records. We conduct linkage when matching records exhibit 1, 2, and 3 errors across the four fields, and when there are 50, 250, and 450 individuals in common across data files. Under each of these settings, we use 100 pairs of simulated data files in order to obtain uncertainty quantification on our performance metrics. We use uniform priors for the $\bm{m}$, $\bm{u}$, and $\pi$ parameters, with $\alpha_{fl} = \beta_{fl} = 1$ for all $f$ and $l$. We run the Gibbs sampler for 1000 iterations, and discard the first 100 as burn-in. We calculate Bayes estimates $\hat{\bm{Z}}$ of the linkage structure using the  loss function and post-processing procedure described in Appendix \ref{bayes-estimate}. Traceplots for parameters of interest for one example simulation are provided in Appendix \ref{app:appendix-sim}; they show no obvious concern over MCMC convergence. We also replicate this simulation allowing \texttt{fabl} to leave some components of the linkage structure undetermined and left for clerical review; those results are in Appendix \ref{partial}.

@@

	Therefore, we perform our analysis with the agreement levels for each field according to Table \ref{Tab:el_salvador_cutoffs_2}. Among the 432 possible agreement patterns, 159 are realized in the data. With this revised comparison specification, \texttt{fabl} runs in 109 seconds, approximately 3 times faster than the \texttt{BRL} run time of 313 seconds.  The estimates of the $\bm{m}$ parameters under each method are similar, as shown in Figure \ref{fig:m-and-u}. Estimates of the $\bm{u}$ parameters are indistinguishable, and thus omitted. Traceplots for parameters of interest are provided in Appendix \ref{app:appendix-es}.

@@

	%We also compute a partial estimate of the linkage structure, using $\theta_{10} = \theta_{01} = 1$, $\theta_{11} = 2$, and $\theta_R = 0.1$ as in the simulation study in Appendix \ref{partial}. Here, the Bayes estimate provides 136 matches of which the model is quite confident, and 175 records to verify manually. This means that after clerical review, the number of individuals replicated across data files would fall in the interval (136, 311), encapsulating the posterior credible interval. More or fewer records could be identified for clerical review by decreasing or increasing $\theta_R$.

@@

	We run a Gibbs sampler for 1000 iterations, taking about 235 seconds. Traceplots do not suggest convergence issues, and are similar to those seen in Appendix \ref{app:appendix-sim} and \ref{app:appendix-es}. As shown in Figure \ref{fig:nltcs-overlap-plot}, the Bayes estimate of the linkage structure has of 9634 matches, with a 95\% credible interval of (9581, 9740). Since we have access to the true linkage structure, we can calculate recall to be 0.89 and precision to be 0.98, resulting in an F-measure of 0.94.

@@

	We provide detailed derivations of the full-conditionals provided in Section 3 of the main text. The $\bm{m}$ and $\bm{u}$ parameters are updated through standard multinomial-Dirichlet distributions. For a particular $m_{fl}$, we have
	\begin{align}
		\mathcal{L}(m_{fl}|\gamma, \bm{u}, \bm{Z}, \pi) &\propto \prod_{i=1}^{n_A} \prod_{j=1}^{n_B} m_{fl}^{I(Z_j = i) I(\gamma_{ij}^f = l) I_{obs}(\gamma_{ij}^f)}  m_{fl}^{\alpha_{fl} - 1} = m_{fl}^{\alpha_{fl}(\bm{Z}) - 1},
	\end{align}
	where $\alpha_{fl}(\bm{Z})= \alpha_{fl} + \sum_{i=1}^{n_A}  \sum_{j=1}^{n_B} I_{obs}(\gamma_{ij}^f)I(\gamma_{ij}^f = l) I(Z_j = i)$. Analogous procedures lead to $\mathcal{L}(u_{fl}| \gamma, \bm{m}, \bm{Z}, \pi)$  $\propto u_{fl}^{\beta_{fl}(\bm{Z}) - 1}$, where $\beta_{fl}(\bm{Z})= \beta_{fl} + \sum_{i=1}^{n_A}  \sum_{j=1}^{n_B} I_{obs}(\gamma_{ij}^f)I(\gamma_{ij}^f = l) I(Z_j \neq i)$. Thus for the vectors of parameters $\bm{m}_f$ and $\bm{u}_f$, we have
	\begin{align}
	\bm{m}_f^{(s+1)}|\gamma, \bm{Z}^{(s)}, \bm{u}^{(s)}, \pi^{(s) &\sim \text{Dirichlet}(\alpha_{f1}(\bm{Z}^{(s)}), \ldots, \alpha_{fL_f}(\bm{Z}^{(s)})), \\
	\bm{u}_f^{(s+1)}|\gamma, \bm{Z}^{(s)}, \bm{m}^{(s)}, \pi^{(s) &\sim \text{Dirichlet}(\beta_{f1}(\bm{Z}^{(s)}), \ldots, \beta_{fL_f}(\bm{Z}^{(s)})).
	\end{align}

@@

	\hypertarget{appendix-sim}{%
		\section{Traceplots for Simulation Study}\label{app:appendix-sim}}
	Figures \ref{fig:sim_overlap_trace}, \ref{fig:sim_m_trace}, and \ref{fig:sim_u_trace} are traceplots for one of the 900 linkage tasks that comprise the simulation in Section 5.2 of the main text. It is set up with one error across the linkage fields and 50 duplicates across files. Traceplots across other settings exhibit similar behavior. Note that traceplots for $\bm{u}$ parameters show very little variation because the overwhelming majority of record pairs are nonmatching.

	\begin{figure}[h]
		\begin{center}
			\includegraphics[width=0.6\textwidth]{../notes/figures/sim_overlap_trace} 
			\caption{Representative traceplot of overlap between files from simulation study in Section 5.2 of the main text.}\label{fig:sim_overlap_trace}
		\end{center}
	\end{figure}

	\begin{figure}
		\begin{center}
			\includegraphics[width=0.6\textwidth]{../notes/figures/sim_m_trace} 
			\caption{Representative traceplot of $\bm{m}$ parameter from simulation study in Section 5.2 of the main text.}\label{fig:sim_m_trace}
		\end{center}
%	\end{figure}

%	\begin{figure}[!h]
		\begin{center}
			\includegraphics[width=0.6\textwidth]{../notes/figures/sim_u_trace} 
			\caption{Representative traceplot of $\bm{u}$ parameters from simulation study in Section 5.2 of the main text.}\label{fig:sim_u_trace}
		\end{center}
	\end{figure}

@@

In this section, we repeat the simulation study in Section 5.2 of the of the main text, allowing for clerical review rather than forcing all records to have or not have links.  Specifically, by leaving $\theta_{10} = \theta_{01} = 1$ and $\theta_{11} = 2$, but setting $\theta_R = 0.1$, we allow the model to decline to decide a match for certain records, with nonassignment being 10\% as costly as a false match. In this context, we are no longer focused on finding all true matches, but rather protecting against false matches. Thus, instead of recall, we use the negative predictive value (NPV), defined as the proportion of non-links that are actual nonmatches. Mathematically, $\text{NPV} = \sum_{j=1}^{n_B} I(\hat{Z}_j = Z_j = n_A + j)$/$\sum_{j=1}^{n_B} I(\hat{Z}_j = n_A + j)$. We continue to use the precision, which is renamed the positive predictive value (PPV) in this context. Lastly, we also examine the rejection rate (RR), or how often the model declines to make a linkage decision, defined as RR = $\sum_{j=1}^{n_B} I(\hat{Z}_j = R)/n_B$. To convey this information alongside NPV and PPV, for which values close to 1 indicate strong performance, we report the decision rate (DR), defined as DR = $1 - RR$.

@@

\begin{figure}
	\begin{center}
		\includegraphics[width=0.99\textwidth]{../notes/figures/sadinle_sim_plot_partial2} 
		\caption{Negative predictive value (NPV), positive predictive value (PPV), and decision rate (DR) on data files in the simulation in Appendix \ref{partial}. We see poorer performance for \texttt{fabl} only in situations with high overlap.}
		\label{fig:sadinle_simulation_partial}
	\end{center}
\end{figure}

@@

	\hypertarget{appendix-speed}{%
	\section{Additional Speed Simulation Study}\label{app:appendix-speed}}
	Figures \ref{fig:app-speed1} and \ref{fig:app-speed2} illustrate that different constructions of the comparison vectors lead to similar speed gains. We replicate the speed study of Section 5.1 of the main text under different settings. Here, we use four fields of comparison, each with three possible levels of agreement, resulting in $3^4 = 81$ possible patterns. The $\bm{m}$ and $\bm{u}$ parameters for this simulation are shown in Table \ref{Tab:distributions_2}.

		\begin{table}[h]
		\centering
		\begin{tabular}{llll|lll}
			\multicolumn{1}{c}{ } & \multicolumn{3}{c}{$\bm{m}$} & \multicolumn{3}{c}{$\bm{u}$} \\
			\cline{2-4} \cline{5-7}
			& Agree & Partial & Disagree & Agree & Partial & Disagree \\
			\hline
			Feature 1 & $\frac{9}{10}$ & $\frac{9}{100}$  & $\frac{1}{100}$ & $\frac{1}{100}$ &  $\frac{3}{100}$ & $\frac{96}{100}$ \\ 
			Feature 2 & $\frac{9}{10}$ & $\frac{9}{100}$  & $\frac{1}{100}$ & $\frac{1}{100}$ &  $\frac{3}{100}$ & $\frac{96}{100}$ \\ 
			Feature 3 & $\frac{9}{10}$ & $\frac{9}{100}$  & $\frac{1}{100}$ & $\frac{1}{100}$ &  $\frac{3}{100}$ & $\frac{96}{100}$ \\ 
			Feature 4 & $\frac{9}{10}$ & $\frac{9}{100}$  & $\frac{1}{100}$ & $\frac{1}{100}$ &  $\frac{3}{100}$ & $\frac{96}{100}$ \\ 
			\hline
		\end{tabular}
		\caption{Probabilities used for $\bm{m}$ and $\bm{u}$ distributions in simulation study in Appendix \ref{app:appendix-speed}.}\label{Tab:distributions_2}
	\end{table}

%	\begin{figure}[h!]
%		\begin{center} \includegraphics[width=0.6\textwidth]{../notes/figures/sadinle_speed_plot2_new} 
%			\caption{Run-time for \texttt{BRL} and \texttt{fabl} to run 1000 Gibbs iterations in simulation study in Appendix \ref{app:appendix-speed}, including hashing step for \texttt{fabl}, for increasing values of both $n_A$ and $n_B$. We see near quadratic growth in run-time for \texttt{BRL}, and near linear growth for \texttt{fabl}.}\label{fig:app-speed1}
%		\end{center}
%	\end{figure}
%	
%	\begin{figure}[h!]
%		\begin{center} \includegraphics[width=0.6\textwidth]{../notes/figures/speed_plot_fixed_nB2_new} 
%			\caption{Run-time for \texttt{BRL} and \texttt{fabl} to run 1000 Gibbs iterations in simulation study in Appendix \ref{app:appendix-speed}, including hashing step for \texttt{fabl}, with increasing $n_A$ and $n_B$ fixed at 500. We see linear growth in run-time for \texttt{BRL}, and near constant run-time for \texttt{fabl}.}\label{fig:app-speed2}
%		\end{center}
%	\end{figure}

	\begin{figure}[h]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=0.95\textwidth]{../notes/figures/sadinle_speed_plot2_new}
		\caption{}
		\label{fig:app-speed1}
	\end{subfigure}%
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=0.95\textwidth]{../notes/figures/speed_plot_fixed_nB2_new} 
		\caption{}
		\label{fig:app-speed2}
	\end{subfigure}
	\caption{Run-time for \texttt{BRL} and \texttt{fabl} to run 1000 Gibbs iterations in simulations described in Appendix \ref{app:appendix-speed}. In (\ref{fig:app-speed1}), both $n_A$ and $n_B$ are increasing. We see quadratic growth in \texttt{BRL} and linear growth in \texttt{fabl}. In (\ref{fig:app-speed2}), only $n_A$ only is increasing. We see linear growth in \texttt{BRL} and approximately constant run-time in \texttt{fabl}.}
	\label{fig:app-speed_sims}
\end{figure}

>>>>

We estimate the posterior distribution of the parameters in (\ref{eqn:likelihood} - \ref{eqn:pi}) using a Gibbs sampler. Supplement \ref{app:derivations} presents derivations for the full conditional distributions. We initialize $\bm{m}$, $\bm{u}$ and $\pi$ from random draws from their prior distributions, and initialize $\bm{Z}$ to reflect no matches across data files; that is, $\bm{Z} = (n_A + 1, \ldots, n_A + n_B)$. Denote the current draw of the sampler by $(s)$ and the updated draw by $(s+1)$. To update $\bm{m}_f$ and $\bm{u}_f$ for all $f = 1, \ldots, F$, we sample
\begin{subequations}
\begin{align}
	\bm{m}_f^{(s+1)}|\gamma, \bm{Z}^{(s)}, \bm{u}^{(s)}, \pi^{(s)} &\sim \text{Dirichlet}(\alpha_{f1}(\bm{Z}^{(s)}), \ldots, \alpha_{fL_f}(\bm{Z}^{(s)})), \label{eqn:m_update} \\
	\bm{u}_f^{(s+1)}|\gamma, \bm{Z}^{(s)}, \bm{m}^{(s)}, \pi^{(s)} &\sim \text{Dirichlet}(\beta_{f1}(\bm{Z}^{(s)}), \ldots, \beta_{fL_f}(\bm{Z}^{(s)})), \label{eqn:u_update} \\
	\text{where }\alpha_{fl}(\bm{Z}^{(s)})&= \alpha_{fl} + \sum_{i=1}^{n_A}\sum_{j=1}^{n_B} I_{obs}(\gamma_{ij}^f) I(\gamma_{ij}^f = l) I(Z_j^{(s)} = i), \label{eqn:alpha_update} \\
	\text{and } \beta_{fl}(\bm{Z}^{(s)})&=  \beta_{fl} + \sum_{i=1}^{n_A}\sum_{j=1}^{n_B}  I_{obs}(\gamma_{ij}^f) I(\gamma_{ij}^f = l) I(Z_j^{(s)} \neq i) \label{eqn:beta_update}.
	%where $\alpha_{fl}(\bm{Z}^{(s)})= \alpha_{fl} + \sum_{i,j} I_{obs}(\gamma_{ij}^f) I(\gamma_{ij}^f = l) I(Z_j^{(s)} = i)$, and $\beta_{fl}(\bm{Z}^{(s)})= \\ \beta_{fl} + \sum_{i,j} I_{obs}(\gamma_{ij}^f) I(\gamma_{ij}^f = l) I(Z_j^{(s)} \neq i)$.
\end{align}
\end{subequations}
Next, we sample $\pi$ from its full conditional, given by
\begin{align}
	\pi^{(s+1)}|\gamma, \bm{Z}^{(s)}, \bm{m}^{(s+1)}, \bm{u}^{(s+1)} \sim  \text{Beta}(n_{AB}(\bm{Z}^{(s)}) + \alpha_{\pi}, n_B - n_{AB}(\bm{Z}^{(s)}) + \beta_{\pi}).
\end{align}
where $n_{AB}(\bm{Z}^{(s)}) = \sum_{j=1}^{n_B} I(Z_j^{(s)} \leq n_A)$.

@@

Finally, to obtain an estimate $\hat{\bm{Z}}$ of the linkage structure, we use the loss functions and Bayes estimate from \cite{sadinle_bayesian_2017}. Since (\ref{eqn:fast_beta_prior}) does not strictly enforce one-to-one matching, it is possible for this Bayes estimate to link multiple records in $B$ to one record in $A$. To obtain a Bayes estimate that fulfills the bipartite requirement, we minimize the expected loss subject to the constraint that $\hat{Z}_j \neq \hat{Z}_{j'}$ for all $j \neq j'$. See Supplement \ref{bayes-estimate} for details redarding the initial Bayes estimate and this post-processing procedure.

@@

We then map the integers in \eqref{eqn:hashing} to sequential integers $\{1, \ldots, P\}$. Denote each unique agreement pattern as $h_p = (h_p^1, \ldots, h_p^F)$, and the set of unique agreement patterns as $\mathcal{P} = \{h_1, \ldots, h_P\}$. When the $(i,j)$ record pair exhibits agreement pattern $p$, we say $\gamma_{ij} = h_p$. In calculations, we will at times use the one-hot encoding of agreement pattern $h_p$, denoted $e(h_p)$. This is a vector of length $\sum_{f=1}^F L_f$ in which the $l + \sum_{k=1}^{f-1} L_k$ component is 1 when $\gamma_{ij}^f = l$, and 0 otherwise. 
%A more complete example of the one-hot encoding is provided in Supplement \ref{app:ohe}.

@@

	In Figure \ref{fig:speed2}, where we fix $n_B = 500$, we see near linear growth for the run-time under \texttt{BRL} as $n_A$ increases, and much more static run-time under \texttt{fabl}. The slight increases in run-time for \texttt{fabl} are due primarily to the hashing step, which again can be run in parallel for large data. To illustrate that these trends are generalizeable to other specifications of the comparison vectors, we have included the run-time results for an additional simulation study, under different comparison vector settings, in Supplement \ref{app:appendix-speed}.

@@

	We create comparison vectors according to the default settings of the \texttt{compareRecords} function from the \texttt{BRL} package, shown in Table \ref{Tab:sadinle_simulation_cutoffs}. Each simulation identifies matched individuals between two data files, each with 500 records. We conduct linkage when matching records exhibit 1, 2, and 3 errors across the four fields, and when there are 50, 250, and 450 individuals in common across data files. Under each of these settings, we use 100 pairs of simulated data files in order to obtain uncertainty quantification on our performance metrics. We use uniform priors for the $\bm{m}$, $\bm{u}$, and $\pi$ parameters, with $\alpha_{fl} = \beta_{fl} = 1$ for all $f$ and $l$. We run the Gibbs sampler for 1000 iterations, and discard the first 100 as burn-in. We calculate Bayes estimates $\hat{\bm{Z}}$ of the linkage structure using the  loss function and post-processing procedure described in Supplement \ref{bayes-estimate}. Traceplots for parameters of interest for one example simulation are provided in Supplement \ref{app:appendix-sim}; they show no obvious concern over MCMC convergence. We also replicate this simulation allowing \texttt{fabl} to leave some components of the linkage structure undetermined and left for clerical review; those results are in Supplement \ref{partial}.

@@

	Therefore, we perform our analysis with the agreement levels for each field according to Table \ref{Tab:el_salvador_cutoffs_2}. Among the 432 possible agreement patterns, 159 are realized in the data. With this revised comparison specification, \texttt{fabl} runs in 109 seconds, approximately 3 times faster than the \texttt{BRL} run time of 313 seconds.  The estimates of the $\bm{m}$ parameters under each method are similar, as shown in Figure \ref{fig:m-and-u}. Estimates of the $\bm{u}$ parameters are indistinguishable, and thus omitted. Traceplots for parameters of interest are provided in Supplement \ref{app:appendix-es}.

@@

	%We also compute a partial estimate of the linkage structure, using $\theta_{10} = \theta_{01} = 1$, $\theta_{11} = 2$, and $\theta_R = 0.1$ as in the simulation study in Supplement \ref{partial}. Here, the Bayes estimate provides 136 matches of which the model is quite confident, and 175 records to verify manually. This means that after clerical review, the number of individuals replicated across data files would fall in the interval (136, 311), encapsulating the posterior credible interval. More or fewer records could be identified for clerical review by decreasing or increasing $\theta_R$.

@@

	We run a Gibbs sampler for 1000 iterations, taking about 235 seconds. Traceplots do not suggest convergence issues, and are similar to those seen in Supplement \ref{app:appendix-sim} and \ref{app:appendix-es}. As shown in Figure \ref{fig:nltcs-overlap-plot}, the Bayes estimate of the linkage structure has of 9634 matches, with a 95\% credible interval of (9581, 9740). Since we have access to the true linkage structure, we can calculate recall to be 0.89 and precision to be 0.98, resulting in an F-measure of 0.94.

@@

	We provide detailed derivations of the full-conditionals provided in Section \ref{sec:fast-beta-linkage}. The $\bm{m}$ and $\bm{u}$ parameters are updated through standard multinomial-Dirichlet distributions. For a particular $m_{fl}$, we have
	\begin{align}
		\mathcal{L}(m_{fl}|\gamma, \bm{u}, \bm{Z}, \pi) &\propto \prod_{i=1}^{n_A} \prod_{j=1}^{n_B} m_{fl}^{I(Z_j = i) I(\gamma_{ij}^f = l) I_{obs}(\gamma_{ij}^f)}  m_{fl}^{\alpha_{fl} - 1} = m_{fl}^{\alpha_{fl}(\bm{Z}) - 1},
	\end{align}
	where $\alpha_{fl}(\bm{Z})= \alpha_{fl} + \sum_{i=1}^{n_A}  \sum_{j=1}^{n_B} I_{obs}(\gamma_{ij}^f)I(\gamma_{ij}^f = l) I(Z_j = i)$. Analogous procedures lead to $\mathcal{L}(u_{fl}| \gamma, \bm{m}, \bm{Z}, \pi)$  $\propto u_{fl}^{\beta_{fl}(\bm{Z}) - 1}$, where $\beta_{fl}(\bm{Z})= \beta_{fl} + \sum_{i=1}^{n_A}  \sum_{j=1}^{n_B} I_{obs}(\gamma_{ij}^f)I(\gamma_{ij}^f = l) I(Z_j \neq i)$. Thus for the vectors of parameters $\bm{m}_f$ and $\bm{u}_f$, we have
	\begin{align}
	\bm{m}_f^{(s+1)}|\gamma, \bm{Z}^{(s)}, \bm{u}^{(s)}, \pi^{(s) &\sim \text{Dirichlet}(\alpha_{f1}(\bm{Z}^{(s)}), \ldots, \alpha_{fL_f}(\bm{Z}^{(s)})), \\
	\bm{u}_f^{(s+1)}|\gamma, \bm{Z}^{(s)}, \bm{m}^{(s)}, \pi^{(s) &\sim \text{Dirichlet}(\beta_{f1}(\bm{Z}^{(s)}), \ldots, \beta_{fL_f}(\bm{Z}^{(s)})).
	\end{align}

@@

	\hypertarget{appendix-sim}{%
		\section{Traceplots for Simulation Study}\label{app:appendix-sim}}
	Figures \ref{fig:sim_overlap_trace}, \ref{fig:sim_m_trace}, and \ref{fig:sim_u_trace} are traceplots for one of the 900 linkage tasks that comprise the simulation in Section \ref{accuracy}. It is set up with one error across the linkage fields and 50 duplicates across files. Traceplots across other settings exhibit similar behavior. Note that traceplots for $\bm{u}$ parameters show very little variation because the overwhelming majority of record pairs are nonmatching.

	\begin{figure}[h]
		\begin{center}
			\includegraphics[width=0.6\textwidth]{../notes/figures/sim_overlap_trace} 
			\caption{Representative traceplot of overlap between files from simulation study in Section \ref{accuracy}.}\label{fig:sim_overlap_trace}
		\end{center}
	\end{figure}

	\begin{figure}
		\begin{center}
			\includegraphics[width=0.6\textwidth]{../notes/figures/sim_m_trace} 
			\caption{Representative traceplot of $\bm{m}$ parameter from simulation study in Section \ref{accuracy}.}\label{fig:sim_m_trace}
		\end{center}
%	\end{figure}

%	\begin{figure}[!h]
		\begin{center}
			\includegraphics[width=0.6\textwidth]{../notes/figures/sim_u_trace} 
			\caption{Representative traceplot of $\bm{u}$ parameters from simulation study in Section \ref{accuracy}.}\label{fig:sim_u_trace}
		\end{center}
	\end{figure}

@@

In this section, we repeat the simulation study in Section \ref{accuracy}, allowing for clerical review rather than forcing all records to have or not have links.  Specifically, by leaving $\theta_{10} = \theta_{01} = 1$ and $\theta_{11} = 2$, but setting $\theta_R = 0.1$, we allow the model to decline to decide a match for certain records, with nonassignment being 10\% as costly as a false match. In this context, we are no longer focused on finding all true matches, but rather protecting against false matches. Thus, instead of recall, we use the negative predictive value (NPV), defined as the proportion of non-links that are actual nonmatches. Mathematically, $\text{NPV} = \sum_{j=1}^{n_B} I(\hat{Z}_j = Z_j = n_A + j)$/$\sum_{j=1}^{n_B} I(\hat{Z}_j = n_A + j)$. We continue to use the precision, which is renamed the positive predictive value (PPV) in this context. Lastly, we also examine the rejection rate (RR), or how often the model declines to make a linkage decision, defined as RR = $\sum_{j=1}^{n_B} I(\hat{Z}_j = R)/n_B$. To convey this information alongside NPV and PPV, for which values close to 1 indicate strong performance, we report the decision rate (DR), defined as DR = $1 - RR$.

@@

\begin{figure}
	\begin{center}
		\includegraphics[width=0.99\textwidth]{../notes/figures/sadinle_sim_plot_partial2} 
		\caption{Negative predictive value (NPV), positive predictive value (PPV), and decision rate (DR) on data files in the simulation in Supplement \ref{partial}. We see poorer performance for \texttt{fabl} only in situations with high overlap.}
		\label{fig:sadinle_simulation_partial}
	\end{center}
\end{figure}

@@

	\hypertarget{appendix-speed}{%
	\section{Additional Speed Simulation Study}\label{app:appendix-speed}}
	Figures \ref{fig:app-speed1} and \ref{fig:app-speed2} illustrate that different constructions of the comparison vectors lead to similar speed gains. We replicate the speed study of Section \ref{speed} under different settings. Here, we use four fields of comparison, each with three possible levels of agreement, resulting in $3^4 = 81$ possible patterns. The $\bm{m}$ and $\bm{u}$ parameters for this simulation are shown in Table \ref{Tab:distributions_2}.

		\begin{table}[h]
		\centering
		\begin{tabular}{llll|lll}
			\multicolumn{1}{c}{ } & \multicolumn{3}{c}{$\bm{m}$} & \multicolumn{3}{c}{$\bm{u}$} \\
			\cline{2-4} \cline{5-7}
			& Agree & Partial & Disagree & Agree & Partial & Disagree \\
			\hline
			Feature 1 & $\frac{9}{10}$ & $\frac{9}{100}$  & $\frac{1}{100}$ & $\frac{1}{100}$ &  $\frac{3}{100}$ & $\frac{96}{100}$ \\ 
			Feature 2 & $\frac{9}{10}$ & $\frac{9}{100}$  & $\frac{1}{100}$ & $\frac{1}{100}$ &  $\frac{3}{100}$ & $\frac{96}{100}$ \\ 
			Feature 3 & $\frac{9}{10}$ & $\frac{9}{100}$  & $\frac{1}{100}$ & $\frac{1}{100}$ &  $\frac{3}{100}$ & $\frac{96}{100}$ \\ 
			Feature 4 & $\frac{9}{10}$ & $\frac{9}{100}$  & $\frac{1}{100}$ & $\frac{1}{100}$ &  $\frac{3}{100}$ & $\frac{96}{100}$ \\ 
			\hline
		\end{tabular}
		\caption{Probabilities used for $\bm{m}$ and $\bm{u}$ distributions in simulation study in Supplement \ref{app:appendix-speed}.}\label{Tab:distributions_2}
	\end{table}

%	\begin{figure}[h!]
%		\begin{center} \includegraphics[width=0.6\textwidth]{../notes/figures/sadinle_speed_plot2_new} 
%			\caption{Run-time for \texttt{BRL} and \texttt{fabl} to run 1000 Gibbs iterations in simulation study in Supplement \ref{app:appendix-speed}, including hashing step for \texttt{fabl}, for increasing values of both $n_A$ and $n_B$. We see near quadratic growth in run-time for \texttt{BRL}, and near linear growth for \texttt{fabl}.}\label{fig:app-speed1}
%		\end{center}
%	\end{figure}
%	
%	\begin{figure}[h!]
%		\begin{center} \includegraphics[width=0.6\textwidth]{../notes/figures/speed_plot_fixed_nB2_new} 
%			\caption{Run-time for \texttt{BRL} and \texttt{fabl} to run 1000 Gibbs iterations in simulation study in Supplement \ref{app:appendix-speed}, including hashing step for \texttt{fabl}, with increasing $n_A$ and $n_B$ fixed at 500. We see linear growth in run-time for \texttt{BRL}, and near constant run-time for \texttt{fabl}.}\label{fig:app-speed2}
%		\end{center}
%	\end{figure}

	\begin{figure}[h]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=0.95\textwidth]{../notes/figures/sadinle_speed_plot2_new}
		\caption{}
		\label{fig:app-speed1}
	\end{subfigure}%
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=0.95\textwidth]{../notes/figures/speed_plot_fixed_nB2_new} 
		\caption{}
		\label{fig:app-speed2}
	\end{subfigure}
	\caption{Run-time for \texttt{BRL} and \texttt{fabl} to run 1000 Gibbs iterations in simulations described in Supplement \ref{app:appendix-speed}. In (\ref{fig:app-speed1}), both $n_A$ and $n_B$ are increasing. We see quadratic growth in \texttt{BRL} and linear growth in \texttt{fabl}. In (\ref{fig:app-speed2}), only $n_A$ only is increasing. We see linear growth in \texttt{BRL} and approximately constant run-time in \texttt{fabl}.}
	\label{fig:app-speed_sims}
\end{figure}
